---
title: "mzhang25_final"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
#load the packages that we need.
library(caret)
library(class)
library(dummies)
library(tidyverse) 
library(factoextra)
library(ggplot2)
library(cluster)
library(GGally)
#Load in the house data
house <- read.csv("C:/Users/Administrator/Desktop/data.csv")
#check and remove all missing data.
house<-na.omit(house)
#for the data 1(date)15(street)17(statezip)18(country)are useless for analyse.
head(house)
data<-house[,c(-1,-15,-17,-18)]
#Plot the graph shows the price change with city.
data%>%filter(price!=0)%>%group_by(city)%>%summarise(price=mean(price)/1000)%>%
ggplot(aes(y = price,x = reorder(city, -price),group=1))+geom_line(fill = 'green')+
xlab('city')+ylab('Price (K)')+geom_area(fill='green')+geom_point()+
theme(axis.text.x = element_text(angle=90))
#shows the frequency of sqft house and check their percentage. 
hist(data$sqft_living)
house_sqft<-ifelse(data$sqft_living<=2000,"small house",ifelse(data$sqft_living<=4000,"medium house","large house"))
freq<-data.frame(table(house_sqft))
freq$percentage<-paste(round(freq$Freq/nrow(norm)*100,2),"%")
freq
#plot histogram.
hist(data$yr_built, breaks = 10, col = "green", main = "Histogram of yr_built", xlab = "Height Bin")
```
```{r}
# We need to normalize all the continuous variables for later cluster.
norm_data<- preProcess(data, method=c("center", "scale"))
norm<-predict(norm_data,data)

#First look at the sqft of living and other area.
#I want to use  sqft of living to do the cluster ( sqft_living+sqft_lot+sqft_above+sqft_basement)
norm_sqft<-norm[,c(4,5,10,11)]
set.seed(1234)
distance <- get_dist(norm_sqft)
fviz_dist(distance)
fviz_nbclust(norm_sqft, kmeans, method = "wss")
fviz_nbclust(norm_sqft, kmeans, method = "silhouette")
# BY using the elbow method, we get k = 5.
kmodel_sqft<- kmeans(norm_sqft, centers = 5, nstart = 25)
kmodel_sqft$centers
kmodel_sqft$size
kmodel_sqft
fviz_cluster(kmodel_sqft,data=norm_sqft)
#The first cluster "single house".
#The second cluster "luxury house".
#the third cluster"general family".
#the forth cluster"gengeral family with large garden".
#the fifth cluster"large house".


# plot the price and condition with cluster fill.
fvizgg<-ggplot(data = norm, mapping = aes(x = price,y = condition, color = factor(kmodel_sqft$cluster)))
fvizgg <- fvizgg + geom_point(pch = 20, size = 3)
fvizgg+ scale_colour_manual(values = c("red","blue","yellow","green","black"))
#table the price with cluster_sqft.
table(norm$city,kmodel_sqft$cluster)
#calculate the mean sqft.
aggregate(house$sqft_living,list(kmodel_sqft$cluster),mean)
```
```{r}
#Second look at house condition. 
#i will use condition and year od bulit and year of renovated to do cluster (condition+yr_year+yr_renovated)
norm_condition<-norm[,c(9,12,13)]
set.seed(1234)
distance <- get_dist(norm_condition)
fviz_dist(distance)
fviz_nbclust(norm_condition, kmeans, method = "wss")
fviz_nbclust(norm_condition, kmeans, method = "silhouette")
#  using the elbow method, we get k = 10.
kmodel_condition<- kmeans(norm_condition, centers = 10, nstart = 25)
kmodel_condition$centers
kmodel_condition$size
kmodel_condition
fviz_cluster(kmodel_condition,data=norm_condition)

 table(data$city,kmodel_condition$cluster)
#cluster1-good condition,new house and no renovated recent.
#cluster2-good condition,old house and have renovated recent.
#cluster3-bad condition,new house and no renovated recent.
#cluster4-bad condition,old house and have renovated recent.
#cluster5-good condition,old house and have renovated recent.
#cluster6-bad condition,old house and have renovated recent.
#cluster7-good condition,new house and have renovated recent.
#cluster8-good condition,old house and no renovated recent.
#cluster9-good condition,old house and no renovated recent.
#cluster10-bad condition,new house and have renovated recent.
#plot the price with condition.
fvizgg<-ggplot(data = norm, mapping = aes(x = price,y = condition, color = factor(kmodel_condition$cluster)))
fvizgg <- fvizgg + geom_point(pch = 20, size = 3)
fvizgg+ scale_colour_manual(values = c("red","blue","yellow","green","black","pink","purple","orange","grey","brown"))
```
```{r}
#Third cluster by using linear model and k-means,to assign a certain supervised performance to the unsupervised model.
#linear model can be a good way to filter important variables. A linear regression model was fitted to the data and l selection of the significant features with high scores.
house <- house%>%filter(price!=0)%>%mutate(price=log(price))
data_predict<-house[,c(-1,-15,-16,-17,-18)]
#separate to train and test to do linear model.
samp<-sample(1:nrow(data_predict),0.8*nrow(data_predict))
train<-data_predict[samp,]
test<-data_predict[-samp,]
#linear model 
fit.lm<-lm(price~.,data=train)
summary(fit.lm)
# use step to do better linear model.
fit.lm2<-step(fit.lm)
summary(fit.lm2)
# prediction
pred.lm<-predict(fit.lm2,test)
plot(pred.lm,test$price)
abline(a=0,b=1,col=2,lty=2)
#greatest impact on the house price are bedrooms, bathrooms and sqft_ living,sqft_lot, floors, view ,yr_built and condition.
#MSE
sum((pred.lm-test$price)^2)

#use important variable from linear model to do the cluster. 
norm_total<-norm[,c(-7,-13,-14)]
set.seed(1234)
distance <- get_dist(norm_total)
fviz_dist(distance)
fviz_nbclust(norm_total, kmeans, method = "wss")
fviz_nbclust(norm_total, kmeans, method = "silhouette")
# By using the elbow method, we get k = 3
kmodel_total<- kmeans(norm_total, centers = 3, nstart = 25)
kmodel_total$centers
kmodel_total$size
kmodel_total
fviz_cluster(kmodel_total,data=norm_total)
#plot the city and price with cluster 3.
table(data$city,kmodel_total$cluster)
table(data$price,kmodel_total$cluster)
#cluster1-high price,lot of bedroom and bathroom,large sqft of living and lot,more floor and view,good condition,large sqft_above,samll sqft_basement,old build.
#cluster2-regular price, large amount bedroom and bathroom,big sqft of living and lot,large amount floor,bad view,bad condition,small sqft_above,small sqft_basement,new build.
#cluster3-low price,small amount bedroom and bathroom,small sqft of living and lot,more floor waterfront and view,bad condition,small sqft_above,large sqft_basement,old build.
```

#use silhouette to check the result of total cluster
sil<-silhouette(kmodel_total$cluster,distance)
summary(sil)$clus.avg.widths
#cluster2 better than cluster 3 and cluster 1.

#check the cluster3 relation with price and sqft.
p<-ggplot(data = norm, mapping = aes(x = price,y = sqft_living, color = factor(kmodel_total$cluster)))
p <- p + geom_point(pch = 20, size = 3)
p + scale_colour_manual(values = c("red","blue","yellow"))



